---
title: "emorsa_bda"
author: "MH Tessler & Yang Wu"
date: "9/17/2021"
output: pdf_document
---

```{r libaries}
library(tidyverse)
library(tidyboot)
library(ggplot2)
library(ggthemes)
library(knitr)
library(coda)
library(viridis)
library(here)
library(patchwork)
theme_set(theme_few())
```

```{r helper fns}
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hpd_upper <- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hpd_lower <- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

count_summary_fn <- function(x) x %>%
  summarize(n = n()) %>%
  mutate(stat = n / sum(n))

mean_ci_funs <- list("ci_lower" = ci_lower, "mean" = mean, "ci_upper" = ci_upper)
```

# Load human data

## State

```{r}
h_state <- read_csv(here("/data/clean_data_true_state.csv"))

h_state_summary <- h_state %>%
  rename(emo = exp, 
         state = response, 
         manipulation = condition_name, 
         manipulation_level = condition_level) %>%
  mutate(manipulation_level = ifelse(manipulation_level=="inf_goal", "inf", manipulation_level),
         manipulation_level = ifelse(manipulation_level=="soc_goal", "soc", manipulation_level))%>%
  group_by(manipulation, manipulation_level, utt, emo, state) %>%
  tidyboot(summary_function = count_summary_fn,
          statistics_functions = function(x) x %>%
          summarise(across(stat, mean_ci_funs, .names = "{.fn}")))

          summarise(across(stat, mean_ci_funs)))
```

Distributions of responses

```{r}
# for (var in unique(h_state_summary$manipulation)) {
#     i <- i + 1 
#     plot[i] <- h_state_summary[h_state_summary$manipulation == var,] %>%
#       ggplot(., aes( x = state, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
#       geom_col(position = position_dodge())+
#       geom_linerange(position = position_dodge())+
#       facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
#     #ggsave(here(paste("/models/figures/mb7_state_inference_", var, ".pdf", sep="")), width = 8, height = 6)
# }
plot_state_emoIsComm <- h_state_summary[h_state_summary$manipulation == "emoIsComm_manipulation",] %>%
      ggplot(., aes( x = state, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("emoIsComm manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_state_goal <- h_state_summary[h_state_summary$manipulation == "goal_manipulation",] %>%
      ggplot(., aes( x = state, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("goal manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_state_state <- h_state_summary[h_state_summary$manipulation == "state_manipulation",] %>%
      mutate(manipulation_level = factor(manipulation_level, levels = c("bad", "no_info", "good"))) %>%
      ggplot(., aes( x = state, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("state manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_state_inference <- plot_state_state + plot_state_goal + plot_state_emoIsComm
ggsave(here(paste("/models/figures/mb7_state_inference.pdf")), width = 12, height = 6)
```

## Goals

```{r}
h_goal <- read_csv(here("/data/clean_data_goals.csv"))

h_goal_summary <- h_goal %>%
  rename(emo = exp,
         manipulation = condition_name, 
         manipulation_level = condition_level) %>%
  group_by(manipulation, manipulation_level, utt, emo, question, response) %>%
  tidyboot(summary_function = count_summary_fn,
           statistics_functions = function(x) x %>%
           #summarise(across(stat, mean_ci_funs, .names = "{.fn}")))
           summarise(across(stat, mean_ci_funs)))
h_info_summary <- h_goal_summary[h_goal_summary$question=="informational goal",]
h_soc_summary <- h_goal_summary[h_goal_summary$question=="social goal",]
```

Distributions of responses

```{r}
# informational goals
plot_info_emoIsComm <- h_info_summary[h_info_summary$manipulation == "emoIsComm_manipulation",] %>%
      ggplot(., aes( x = response, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("emoIsComm manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_info_goal <- h_info_summary[h_info_summary$manipulation == "goal_manipulation",] %>%
      ggplot(., aes( x = response, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("goal manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_info_state <- h_info_summary[h_info_summary$manipulation == "state_manipulation",] %>%
      mutate(manipulation_level = factor(manipulation_level, levels = c("bad", "no_info", "good"))) %>%
      ggplot(., aes( x = response, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("state manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_info_inference <- plot_info_state + plot_info_goal + plot_info_emoIsComm
ggsave(here(paste("/models/figures/mb7_info_inference.pdf")), width = 12, height = 6)

# social goals
plot_soc_emoIsComm <- h_soc_summary[h_soc_summary$manipulation == "emoIsComm_manipulation",] %>%
      ggplot(., aes( x = response, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("emoIsComm manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_soc_goal <- h_soc_summary[h_soc_summary$manipulation == "goal_manipulation",] %>%
      ggplot(., aes( x = response, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("goal manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_soc_state <- h_soc_summary[h_soc_summary$manipulation == "state_manipulation",] %>%
      mutate(manipulation_level = factor(manipulation_level, levels = c("bad", "no_info", "good"))) %>%
      ggplot(., aes( x = response, y = stat_mean, ymin = stat_ci_lower, ymax = stat_ci_upper))+
      geom_col(position = position_dodge())+
      geom_linerange(position = position_dodge())+
      ggtitle("state manipulation")+
      theme(plot.title = element_text(hjust = 0.5))+
      facet_grid(rows=vars(utt, emo), cols=vars(manipulation_level))
plot_soc_inference <- plot_soc_state + plot_soc_goal + plot_soc_emoIsComm
ggsave(here(paste("/models/figures/mb7_soc_inference.pdf")), width = 12, height = 6)

```

# Load model results

```{r}
results_path <- "models/bda_results/"
model.files <- list.files(
      path = paste(here(), results_path, sep = "/"),
      pattern = "bda-M"
    )
df.m <- map_dfr(model.files, function(model.file){
    read_csv(here(paste(results_path, model.file, sep = "")),
             col_types = cols(
                      iter = col_double(),
                      model = col_character(),
                      chain = col_double(),
                      manipulation = col_character(),
                      manipulation_level = col_character(),
                      parameter = col_character(),
                      utt = col_character(),
                      emo = col_character(),
                      value = col_character(),
                      prob = col_double(),
                      score = col_double()
                    ))
})
```



# Global parameters

```{r}
df.m %>%
  filter(parameter == "parameter", is.na(emo)) %>%
  ggplot(., aes(x = prob))+
  geom_histogram(position = position_dodge())+
  facet_grid(cols = vars(utt), scales = "free_x")
ggsave(here("/models/figures/mb7_global_parameters.pdf"), width = 8, height = 5)
```

Summary

```{r}
df.m %>%
  filter(parameter == "parameter", is.na(emo)) %>%
  group_by(utt) %>%
  summarize(
    MAP = estimate_mode(prob),
    cred_upper = hpd_upper(prob),
    cred_lower = hpd_lower(prob)
  ) -> df_parameter_summary


df_parameter_summary %>%
  kable(.)
```


# Prior parameters

```{r}
df.m %>%
  filter(parameter == "parameter", is.na(emo) == FALSE) %>%
  ggplot(., aes(x = prob))+
  geom_histogram(position = position_dodge())+
  facet_grid(cols = vars(utt, emo), rows = vars(value), scales = "free_x")
ggsave(here("/models/figures/mb7_prior_parameters.pdf"), width = 20, height = 5)
```

Summary

```{r}
df.m %>%
  filter(parameter == "parameter", is.na(emo) == FALSE) %>%
  group_by(utt, emo, value) %>%
  summarize(
    MAP = estimate_mode(prob),
    cred_upper = hpd_upper(prob),
    cred_lower = hpd_lower(prob)
  ) -> df_parameter_summary


df_parameter_summary %>%
  kable(.)
```


# State posterior predictives

```{r}
df_state <- df.m %>%
  filter(parameter == "state") %>%
  mutate(state = as.numeric(value)) %>%
  select(-value)

df_state_summary <- df_state %>%
  group_by(manipulation, manipulation_level, utt, emo, state) %>%
  summarize(
    MAP = estimate_mode(prob),
    cred_upper = hpd_upper(prob),
    cred_lower = hpd_lower(prob)
  )

```

join with human data

```{r}
md_state <- left_join(
  df_state_summary, h_state_summary
)
```

## posterior predictive scatterplots

correlation table


```{r}
md_state %>%
  unite("utt_emo", utt, emo) %>%
  mutate(
    mean = ifelse(is.na(stat_mean), 0, stat_mean),
    ci_lower = ifelse(is.na(stat_ci_lower), 0, stat_ci_lower),
    ci_upper = ifelse(is.na(stat_ci_upper), 0, stat_ci_upper),
    state = factor(state)
  ) %>%
  #group_by(model) %>%
  summarize(
    mse = mean((MAP - mean)^2),
    r = cor(MAP, mean),
    r2 = r^2
  ) -> md_state_corr_table

#write_csv(md_state_corr_table, "../state_correlations.csv")

md_state_corr_table %>%
  kable()
```

```{r}
md_state %>%
  unite("utt_emo", utt, emo) %>%
  mutate(
    mean = ifelse(is.na(stat_mean), 0, stat_mean),
    ci_lower = ifelse(is.na(stat_ci_lower), 0, stat_ci_lower),
    ci_upper = ifelse(is.na(stat_ci_upper), 0, stat_ci_upper),
    state = factor(state)
  ) %>%
  ggplot(., aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
                      y = mean, ymin = ci_lower, ymax = ci_upper,
                 shape = utt_emo, color = state))+
  geom_abline(intercept = 0, slope = 1, alpha = 0.3, linetype = 2)+
  geom_linerange()+
  geom_text(data = md_state_corr_table, x = 0.15, y = 0.93,
            aes(label = paste("r=", round(r, 2), sep= "")),
            inherit.aes = F)+
  ggstance::geom_linerangeh()+
  geom_point()+
  scale_color_viridis(discrete = T)+
  #xlim(0, 1)+
  #ylim(0, 1)+
  coord_fixed()+
  #facet_wrap(~model, nrow = 2)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  theme(legend.position = 'bottom')+
  labs(
    x = "Model Predicted Probability",
    y = "Human Proportion Selected"
  )

ggsave(filename = "bda_results/figs/bda_scatters_state_21models_cogsci.pdf", width = 18, height = 5)
```





## bar plots

```{r}
bind_rows(
  df_state_summary %>%
   rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper),
  h_state_summary %>%
   select(-n, -empirical_n, -empirical_stat) %>%
   mutate(model = 'human data')
) -> dfh_state_long

bar_width = 0.8
dfh_state_long %>%
  unite("utt_emo", utt, emo) %>%
  mutate( state = factor(state)) %>%
  ggplot(., aes( x = utt_emo, y = mean, ymin = ci_lower, ymax = ci_upper,
                 fill = state))+
    geom_col(position = position_dodge(bar_width), width = bar_width,
             color = 'black') +
    geom_linerange(position = position_dodge(bar_width))+
  # facet_grid(utt_emo~model)+
  facet_wrap(~model, nrow = 3)+
  scale_fill_viridis( discrete = T )+
  guides(fill = F)+
  theme(strip.text.y = element_text(angle = 0),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  ylab("Predicted probability / Empirical proportion")

ggsave(filename = "bda_results/figs/bda_bars_state_22models_cogsci.pdf", width = 24, height = 7)
```

## paper plot: focus on Mb7

### full distribution

```{r}
dfh_state_long %>%
    filter(model %in% c("Mb6_UttBalEmoTruSoc", "Mb2_UttBalEmoBal", "Mb7_UttBalEmoTruBal", "human data")) %>%
    unite("utt_emo", utt, emo) %>%
  mutate( state = factor(state),
         model = factor(model, levels = c( "human data", "Mb7_UttBalEmoTruBal", "Mb2_UttBalEmoBal", "Mb6_UttBalEmoTruSoc"),
                         labels = c("Human data", "Model\n(Auto/Soc/Inf)",
                                    "Model\n(Soc/Inf)", "Model\n(Auto/Soc)")),
          utt_emo = factor(utt_emo, levels = c("bad_frown", "bad_smile", "good_frown", "good_smile"),
                           labels = c("Bad :(", "Bad :)","Good :(", "Good :)"))) %>%
  ggplot(., aes( x = state, y = mean, ymin = ci_lower, ymax = ci_upper,
                 fill = state))+
    geom_col(position = position_dodge(bar_width), width = bar_width,
             color = 'black') +
    geom_linerange(position = position_dodge(bar_width))+
  # facet_grid(utt_emo~model)+
  facet_grid(utt_emo~model)+
  scale_fill_viridis( discrete = T, option = "A" )+
  # guides(fill = F)+
  theme(strip.text.y = element_text(angle = 0))+#,
        #axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  ylab("Predicted probability / Empirical proportion")+
  xlab("State")+
  guides(fill = F)

ggsave(filename = "bda_results/figs/bda_states_bars_Mb7_Mb2_Mb6_human_cogsci.pdf", width = 5, height = 4)
```

### expected values

```{r}
df_mb7_expval <- df.m %>%
  filter(parameter == "state", model == "Mb7_UttBalEmoTruBal") %>%
  group_by(model, iter, utt, emo) %>%
  mutate(valprob = as.numeric(value) * prob) %>%
  summarize(expval = sum(valprob)) %>%
  group_by(model, utt, emo) %>%
  summarize(
    MAP = estimate_mode(expval),
    cred_upper = hpd_upper(expval),
    cred_lower = hpd_lower(expval)
  )

h_state %>%
  rename(emo = exp, state = response) %>%
  group_by(utt, emo) %>%
  tidyboot_mean(column = state) -> h_state_expval_summary

# md_expval_state <- left_join(
#   df_mb7_expval, h_state_expval_summary
# )

bind_rows(
  df_mb7_expval %>%
   rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper),
  h_state_expval_summary %>%
   select(-n, -empirical_stat) %>%
   mutate(model = 'human data')
) -> dfh_expval_state_long



dfh_expval_state_long %>%
  unite("utt_emo", utt, emo) %>%
  #$mutate( state = factor(state)) %>%
  ggplot(., aes( x = utt_emo, y = mean, ymin = ci_lower, ymax = ci_upper,
                 group = model))+
    # geom_col(position = position_dodge(bar_width), width = bar_width,
    #          color = 'black') +
  geom_linerange()+
  geom_line()+
  # facet_grid(utt_emo~model)+
  facet_wrap(~model, nrow = 1)+
  #scale_color_viridis( discrete = T )+
  guides(color = F)+
  theme(strip.text.y = element_text(angle = 0),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))+
  ylab("Predicted probability / Empirical proportion")

```


# Goal posterior predictives

```{r}
df_goal <- df.m %>%
  filter(parameter %in% c("socGoal", "infGoal")) %>%
  mutate(rating = as.numeric(value)) %>%
  select(-value)

df_goal_summary <- df_goal %>%
  group_by(model, parameter, utt, emo, rating) %>%
  summarize(
    MAP = estimate_mode(prob),
    cred_upper = hpd_upper(prob),
    cred_lower = hpd_lower(prob)
  )
```


join with human data

```{r}
md_goals <- left_join(
  df_goal_summary %>%
    mutate(question = factor(parameter, levels = c("infGoal", "socGoal"),
                            labels = c("informational goal", "social goal"))),
  h_goal_summary %>% rename(rating = response)
)
```

correlation table

```{r corr table goal}
md_goals %>%
  unite("utt_emo", utt, emo) %>%
  mutate(
    mean = ifelse(is.na(mean), 0, mean),
    ci_lower = ifelse(is.na(ci_lower), 0, ci_lower),
    ci_upper = ifelse(is.na(ci_upper), 0, ci_upper)
  ) %>%
  group_by(model, question) %>%
  summarize(
    n = n(),
    mse = mean((MAP - mean)^2),
    r = cor(MAP, mean),
    r2 = r^2
  ) -> md_goal_corr_table

write_csv(md_goal_corr_table, "../goal_correlations.csv")


md_goal_corr_table %>%
  kable()
```


posterior predictive scatterplot

```{r}
md_goals %>%
  unite("utt_emo", utt, emo) %>%
  mutate(
    mean = ifelse(is.na(mean), 0, mean),
    ci_lower = ifelse(is.na(ci_lower), 0, ci_lower),
    ci_upper = ifelse(is.na(ci_upper), 0, ci_upper),
    rating = factor(rating),
  ) %>%
  ggplot(., aes( x = MAP, xmin = cred_lower, xmax = cred_upper,
                      y = mean, ymin = ci_lower, ymax = ci_upper,
                 shape = utt_emo, color = rating))+
  geom_abline(intercept = 0, slope = 1, alpha = 0.3, linetype = 2)+
  geom_linerange()+
  geom_text(data = md_goal_corr_table, x = 0.15, y = 0.96,
            aes(label = paste("r=", round(r, 2), sep= "")),
            inherit.aes = F)+
  ggstance::geom_linerangeh()+
  geom_point()+
  coord_fixed()+
  facet_grid(question~model)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  theme(legend.position = 'bottom')+
  labs(
    x = "Model Predicted Probability",
    y = "Human Proportion Selected"
  )

ggsave(filename = "bda_results/figs/bda_scatters_goal_21models_cogsci.pdf",
       width = 24, height = 4.5)
```

## bar plots

```{r}
bind_rows(
  df_goal_summary %>%
    mutate(question = factor(parameter, levels = c("infGoal", "socGoal"),
                            labels = c("informational goal", "social goal"))) %>%
   rename(mean = MAP, ci_lower = cred_lower, ci_upper = cred_upper) %>%
    ungroup() %>%
    select(-parameter),
  h_goal_summary %>%
   select(-n, -empirical_n, -empirical_stat) %>%
   mutate(model = 'human data') %>%
   rename(rating = response)
) -> dfh_goal_long



bar_width = 0.8
dfh_goal_long %>%
  unite("utt_emo", utt, emo) %>%
  mutate_at(vars(rating), as.factor) %>%
  ggplot(., aes( x = question, y = mean, ymin = ci_lower, ymax = ci_upper,
                 fill = rating, group = rating))+
  geom_col(position = position_dodge(bar_width), width = bar_width,
             color = 'black') +
  geom_linerange(position = position_dodge(bar_width))+
  facet_grid(utt_emo~model)+
  scale_fill_viridis(discrete = T)+
  #guides(fill = F)+
  theme(strip.text.y = element_text(angle = 0),
        axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1))+
  ylab("Predicted probability / Empirical proportion")

ggsave(filename = "bda_results/figs/bda_bars_goals_21models_cogsci.pdf", width = 30, height = 8)
```

### full distribution

```{r}
dfh_goal_long %>%
  filter(model %in% c("Mb6_UttBalEmoTruSoc", "Mb2_UttBalEmoBal", "Mb7_UttBalEmoTruBal", "human data")) %>%
  unite("utt_emo", utt, emo) %>%
  mutate_at(vars(rating), as.factor) %>%
  mutate( model = factor(model, levels = c( "human data", "Mb7_UttBalEmoTruBal", "Mb2_UttBalEmoBal", "Mb6_UttBalEmoTruSoc"),
                         labels = c("Human data", "Model (Auto/Soc/Inf)",
                                    "Model (Soc/Inf)", "Model (Auto/Soc)")),
          utt_emo = factor(utt_emo, levels = c("bad_frown", "bad_smile", "good_frown", "good_smile"),
                           labels = c("Bad :(", "Bad :)","Good :(", "Good :)"))) %>%
  ggplot(., aes( x = question, y = mean, ymin = ci_lower, ymax = ci_upper,
                 fill = rating, group = rating))+
  geom_col(position = position_dodge(bar_width), width = bar_width,
             color = 'black') +
  geom_linerange(position = position_dodge(bar_width))+
  facet_grid(utt_emo~model)+
  scale_fill_viridis(discrete = T)+
  #guides(fill = F)+
  theme(strip.text.y = element_text(angle = 0),
        axis.text.x = element_text(angle = 20, hjust = 0.6, vjust = 0.7),
        legend.position = 'bottom')+
  ylab("Predicted probability / Empirical proportion")+
  xlab("")

ggsave(filename = "bda_results/figs/bda_goals_bars_Mb7_Mb2_Mb6_human_cogsci.pdf", width = 7, height = 5)
```

# Model Comparison

```{r load model comparison}
ais_results_path <- "results_ais/cogsci/"
model_type_utt <- c("a", "b", "c", "d")
model_type_emo <- 1:8
#comparison_type <- c("allData", "stateOnly")

m.mll <-  map_dfr(model_type_utt, function(mtu){
  map_dfr(model_type_emo, function(mte){
    #Qmap_dfr(comparison_type, function(comp_type){

    model.files <- list.files(
      path = ais_results_path,
      pattern = paste("ais-M", mtu, mte, sep = "")
    )

    map_dfr(model.files, function(model.file){

     read_csv(paste(ais_results_path, model.file, sep = ""),
              col_types = cols(
              model = col_character(),
              stateOnly = col_character(),
              chain = col_character(),
              steps = col_character(),
              iter = col_character(),
              weight = col_character()
            ))

    })

  })

})
```

Distributions of importance sampling weights

```{r}
m.mll %>%
  mutate_at(vars(weight), as.numeric) %>%
  ggplot(., aes ( x = weight ))+
  geom_histogram()+
  facet_grid(stateOnly ~ model, scales = 'free')
```

State only

```{r}
m.mll %>%
  filter(stateOnly == "stateOnly") %>%
  mutate(weight = as.numeric(weight)) %>%
  group_by(model, stateOnly) %>%
  #count()
  summarize(
    n = n(),
    mll = mean(weight),
    min_mll = min(weight),
    max_mll = max(weight),
    range_mll = min_mll - max_mll
  ) -> m.mll_summary_stateOnly

m.mll_summary_stateOnly[with(m.mll_summary_stateOnly, order(-mll)),] %>%
  write_csv(., "../stateOnly.csv")


m.mll_summary_stateOnly %>%
  kable()
```

```{r bayes factor table}
m.mll_summary_stateOnly %>%
  filter(model != "Mb7_UttBalEmoTruBal") %>%
  select(model, stateOnly, mll)  %>%
  cbind(.,
    m.mll_summary_stateOnly %>%
      filter(model == "Mb7_UttBalEmoTruBal") %>%
      #ungroup() %>%
      select(mll) %>%
      rename(mb7 = mll)
  ) %>%
  mutate(log_bf = mll - mb7,
         bf = exp( mb7 - mll)) %>%
  write_csv(., "../stateOnly_bf.csv")

```



```{r}
m.mll_summary_stateOnly %>%
  ungroup() %>%
  mutate(best_mll = max(mll),
         log_ratio = mll - best_mll,
         ratio = exp(log_ratio),
         posterior_prob = ratio / sum(ratio)) %>%
  ggplot(., aes( x = model, y = posterior_prob, fill = posterior_prob)) +
  geom_col(color = 'black')+
  scale_fill_viridis()+
  labs(y = "Model posterior probability")+
  coord_flip()+
  ggtitle("State data only")

ggsave(filename = "bda_results/figs/ais_posterior_probs_stateOnly.pdf",
       width = 7, height = 4.5)
```

States and goals

```{r}
models_for_goals <- c("Ma2_UttInfEmoBal", "Ma6_UttInfEmoTruSoc",
                      "Ma7_UttInfEmoTruBal", "Mb1_UttBalEmoSoc",
                      "Mb2_UttBalEmoBal", "Mb3_UttBalEmoTru",
                      "Mb4_UttBalEmoInf", "Mb5_UttBalEmoTruInf",
                      "Mb6_UttBalEmoTruSoc", "Mb7_UttBalEmoTruBal",
                        "Mb8_UttBalEmoInfSoc",
                        "Mc2_UttInfEmoBal",
                        "Mc7_UttInfEmoTruBal",
                        "Md1_UttBalEmoSoc",
                        "Md4_UttBalEmoInf",
                        "Md5_UttBalEmoTruInf",
                        "Md6_UttBalEmoTruSoc")
m.mll %>%
  filter(stateOnly == "allData", model %in% models_for_goals) %>%
  mutate(weight = as.numeric(weight)) %>%
  group_by(model, stateOnly) %>%
  summarize(
    n = n(),
    mll = mean(weight),
    min_mll = min(weight),
    max_mll = max(weight),
    range_mll = min_mll - max_mll
  ) -> m.mll_summary_allData

m.mll_summary_allData[with(m.mll_summary_allData, order(-mll)),]

m.mll_summary_allData %>%
  kable()
```




```{r bayes factor table}
m.mll_summary_allData %>%
  filter(model != "Mb7_UttBalEmoTruBal") %>%
  select(model, stateOnly, mll)  %>%
  cbind(.,
    m.mll_summary_allData %>%
      filter(model == "Mb7_UttBalEmoTruBal") %>%
      #ungroup() %>%
      select(mll) %>%
      rename(mb7 = mll)
  ) %>%
  mutate(log_bf = mll - mb7,
         bf = exp( mb7 - mll)) %>%
  write_csv(., "../allData_bf.csv")

```


```{r}
m.mll_summary_allData %>%
  ungroup() %>%
  mutate(best_mll = max(mll),
         log_ratio = mll - best_mll,
         ratio = exp(log_ratio),
         posterior_prob = ratio / sum(ratio))  %>% View()
  ggplot(., aes( x = model, y = posterior_prob, fill = posterior_prob)) +
  geom_col(color = 'black')+
  scale_fill_viridis()+
  coord_flip()
```
